---
title: "p8105_hw1_sl4269"
author: "Steven Lawrence"
date: "September 12, 2019"
output: 
  html_document:
    code_folding: hide
    toc: true
    toc_float: true
---

#Problem 1



Neccessary packages

```{r Loading libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
library(dplyr)
```

## Introducing Variable Types and Coercion 

###Data frame 1

```{r Dataframe 1}
data <- tibble(
  rvar = rnorm(8,0,1), #rvar = random variable N(0,1)
  logicv = rvar > 0, #logic vector of rvar > 0
  charv = as.character(rvar[]),#character vector of rvar
  facv = as.factor(
                cut(
                    rvar, 
                    3,
                    levels = c("1","2","3"), 
                    labels = FALSE, 
                    ordered_result = F))  #factor vecor of rvar 
)
```

###Nature of Variable Means
Taking the mean of every variable in dataframe1. 

mean of random, logic, character, and factor variables respectibely. 
```{r Means of data, message=FALSE, warning=FALSE}
mean(pull(data, rvar))
mean(pull(data,logicv))
mean(pull(data,charv))
mean(pull(data, facv))

```
Taking the mean of the character and factor variable did not work. 

###AS.Numeric?
Converting the logic, character, and factor variale using as.numeric.

```{r coverting to numeric, message=FALSE, eval=FALSE}
as.numeric(pull(data,logicv))
as.numeric(pull(data,charv))
as.numeric(pull(data,facv))
```
The logic vector prints as 1's and 0's.  The character vector returns to a number format. Lastly, the factor variable returns the levels as numeric values. 

#Problem 2

## Introducing inline code, and Plots

###Data frame 2

Creating a data frame of random variables.
```{r data frame 2, message=FALSE, warning=FALSE}
data2 <- tibble(
  x = rnorm(500,0,1),
  y = rnorm(500,0,1),
  logic_xy = x + y > 1,
  nlogic_xy = as.numeric(logic_xy),
  flogic_xy = as.factor(logic_xy)
  
  )
```
Here are some discriptive statistics of data2. The size of this data set is `r nrow(data2)` by `r ncol(data2)`. For the variable x, the mean is `r signif(mean(pull(data2,x)),2)`, median ,`r signif(median(pull(data2,x)),2)` and standard deviation is `r signif(sd(pull(data2,x)),2)`. The proportion of `x > y` is `r prop.table(table((pull(data2,x) > pull(data2,y))))[2] `.

###Scatter plots of `x and y`

```{r scatter plot, message=FALSE}
data2 %>% ggplot(aes(x=x,y=y, color = logic_xy))+
  geom_point()+
  labs(color = "Logic vector", title = "X and Y Random Variables Colored by Logic Vector")

data2 %>% ggplot(aes(x=x,y=y, color = nlogic_xy))+
  geom_point()+
  labs(color = "Numeric\nLogic vector",title = "X and Y Random Variables Colored by Numeric Logic Vector")

data2 %>% ggplot(aes(x=x,y=y, color = flogic_xy))+
  geom_point()+
  labs(color = "Factored\nLogic vector",title = "X and Y Random Variables Colored by Factored Logic Vector")



```
In regards to how the variables were colored by the various vectors, I believe the logic vector and the factor factor vector are virtually the same.  The numeric vector introduced decimal values in the scale that are not used. 

###GGsave
Now I will save my ggplot scatter plots `ggsave`.


```{r saving plot with ggsave, message=FALSE, eval=FALSE, warning=FALSE}

ggsave(filename = 'data2.jpeg', device = jpeg, dpi = 260, width = 3, height = 4, scale = 2, units = "in")
```


