---
title: "p8105_hw1_sl4269"
author: "Steven Lawrence"
date: "September 12, 2019"
output: github_document
---

#Problem 1



Neccessary packages

```{r Loading libraries, message=FALSE, warning=FALSE}
library(tidyverse)
library(ggplot2)
```

## Introducing Variable Types and Coercion 

Data frame 

```{r Dataframe 1}
data <- tibble(
  rvar = rnorm(8,0,1), #rvar = random variable N(0,1)
  logicv = rvar > 0, #logic vector of rvar > 0
  charv = as.character(rvar[]),#character vector of rvar
  facv = as.factor(
                cut(
                    rvar, 
                    3,
                    levels = c("1","2","3"), 
                    labels = FALSE, 
                    ordered_result = F))  #factor vecor of rvar 
)
```

Taking the mean of every variable in dataframe1. 

```{r Means of data, message=FALSE, warning=FALSE}
mean(pull(data, rvar))
mean(pull(data,logicv))
mean(pull(data,charv))
mean(pull(data, facv))

```
Taking the mean of the character and factor variable did not work. 

Converting the logic, character, and factor variale using as.numeric.

```{r coverting to numeric, message=FALSE, eval=FALSE}
as.numeric(pull(data,logicv))
as.numeric(pull(data,charv))
as.numeric(pull(data,facv))
```
The logic vector prints as 1's and 0's.  The character vector returns to a number format. Lastly, the factor variable returns the levels as numeric values. 

#Problem 2

## Introducing inline code, and Plots

Creating a data frame

```{r}
data2 <- tibble(
  x = rnorm(500,0,1),
  y = rnorm(500,0,1),
  logic_xy = x + y > 1,
  nlogic_xy = as.numeric(logic_xy),
  flogic_xy = as.factor(logic_xy)
  
  )

head(data2)
```



